Binary companions of red giant stars in \apogee\ \DR

### 2018-02-28 paper/1-catalog/twoface-catalog.tex
Conc

\todo{catalogs available online}, full code open source.\footnote{The code used in this
project is available from \url{https://github.com/adrn/TwoFace} under the MIT
open-source software license.}

@@

It is a pleasure to thank Keith Hawkins (Columbia), XXXXXXX.

@@

\software{
    \package{Astropy} (\citealt{Astropy-Collaboration:2013}),
    \package{emcee} (\citealt{Foreman-Mackey:2013}),
    \package{IPython} (\citealt{Perez:2007}),
    \package{matplotlib} (\citealt{Hunter:2007}),
    \package{numpy} (\citealt{Van-der-Walt:2011}),
    \package{scipy} (\url{https://www.scipy.org/}),
    \package{sqlalchemy} (\url{https://www.sqlalchemy.org/}).
}

@@

>>>>

All companion catalogs described in this work (\sectionname~\ref{sec:catalogs})
are available online at \todo{XX}.
The source code for this project is open source and available from
\url{https://github.com/adrn/TwoFace} under the MIT open source software
license.

@@

It is a pleasure to thank Keith Hawkins (Columbia), \todo{who else?}.

@@

\software{
    \package{Astropy} (\citealt{Astropy-Collaboration:2013}),
    \package{emcee} (\citealt{Foreman-Mackey:2013}),
    \package{IPython} (\citealt{Perez:2007}),
    \package{matplotlib} (\citealt{Hunter:2007}),
    \package{numpy} (\citealt{Van-der-Walt:2011}),
    \package{scipy} (\url{https://www.scipy.org/}),
    \package{schwimmbad} (\todo{JOSS paper}),
    \package{sqlalchemy} (\url{https://www.sqlalchemy.org/}),
    \package{thejoker} (\todo{thejoker zenodo?}),
    \package{twobody} (\todo{twobody zenodo?}).
}

@@

\clearpage
